Batch Bayesian Optimization via Multi-objective Acquisition Ensemble for Automated Analog Circuit Design

### 2018-02-08 paper/experiments.tex

The proposed MACE algorithm was tested using eight benchmark functions and two
real-world circuits. Four state-of-the-art parallel Bayesian optimization
methods were compared, including the BLCB algorithm, the local penalization
method with EI acquisition function, the qEI and qKG methods\footnote{We
implemented the BLCB algorithm as the availble open source implementations only
allow discrete input; for the EI-LP method, the code is downloaded from
https://github.com/SheffieldML/GPyOpt is used; the code for qEI and qKG is
downloaded from https://github.com/wujian16/Cornell-MOE}.

@@

The mean performances of the tested algorithms on the benchmark functions are
plotted in Figure~\ref{fig:CovPlotBenchmark}, the statistics of the final
optimization results are listed in Table~\ref{tab:result_analytical}. As can be
seen in Figure~\ref{fig:CovPlotBenchmark} and
Table~\ref{tab:result_analytical}, when running in sequential mode, the MACE
algorithm is competitive with the LCB and EI acquisition functions, the MACE-1
algorithm gave better performances than EI-1 and LCB-1 in the Eggholder,
Branin, Hartmann6, Ackley10, and Rosenbrock10 functions; also, the parallel
MACE (MACE-4) gave the best performances among all the tested algorithms for
six out of the eight benchmark functions, and has shown dramatic speedup
compared to the sequential MACE (MACE-1).

@@

The operational amplifier~\cite{wang2014enabling} shown in
Figure~\ref{fig:schDAC2014} is used for comparison, the circuit is designed
using the 180nm process. It has ten design parameters, including the lengths
and widths of transistors, the resistance of resistors and the capacitance of
capacitors. The circuit is simulated using the HSPICE circuit simulator.

We want to maximize the gain, unit gain frequency (UGF) and the phase margin (PM) for this amplifier, the $FOM$ is constructed as:
$$
\mathit{FOM} = -1.2 \times \mathit{gain} - 10 \times \mathit{UGF} - 1.6 \times \mathit{PM}
$$

For this circuit, we compared the MACE algorithm with the BLCB and EI-LP
algorithms, the qKG and qEI are not compared as the calculation of qEI and qKG
acquisition functions become very slow for the ten-dimensional functions.

@@

We run the algorithms in sequential mode and batch mode, for the batch mode,
batch size is set to $B = 4$. The number initial random sampling is set to
$N_{init} = 100$, and the number of iterations is set to $N_{iter} = 100$.

@@

The power amplifier shown in Figure~\ref{fig:schPA} is used for comparison, the
circuit is designed using the 180nm process with twelve design parameters, the
circuit is simulated by HSPICE to get its performances.

For this power amplifier, we aim to maximize the power added efficiency (PAE) and the output power (Pout), the $FOM$ is constructed as
$$
\mathit{FOM} = -3 \times \mathit{PAE} - \mathit{Pout}
$$

The MACE, BLCB, and EI-LP algorithms were tested in both sequential and batch
mode. The number of initial sampling is $N_{init} = 100$, the number of
iterations is $N_{iter} = 100$, the batch size is set to $B = 4$, so the total
number of HSPICE simulations is 500 for each batch run and 200 for each
sequential run.

@@

The mean convergence plot is given in Figure~\ref{fig:resClassE}. We can see
that the MACE outperformed the BLCB and EI-LP in both sequential and batch
mode. For the batch runs, the MACE convergences fastest among the three
algorithms, while the sequential MACE has similar performance as the batch
EI-LP method.

>>>>

The proposed MACE algorithm was tested using eight benchmark functions and two
real-world circuits. Four state-of-the-art parallel Bayesian optimization
methods were compared, including the BLCB algorithm, the local penalization
method with EI acquisition function, the qEI and qKG methods\footnote{We
implemented the BLCB algorithm as the available open source implementations only
allow discrete input. For the EI-LP method, the code is downloaded from
https://github.com/SheffieldML/GPyOpt. The code for qEI and qKG is
downloaded from https://github.com/wujian16/Cornell-MOE}.

@@

The mean performances of the tested algorithms on the benchmark functions are
plotted in Figure~\ref{fig:CovPlotBenchmark}, the statistics of the final
optimization results are listed in Table~\ref{tab:result_analytical}. As can be
seen in Figure~\ref{fig:CovPlotBenchmark} and
Table~\ref{tab:result_analytical}, when running in sequential mode, the MACE
algorithm is competitive with the LCB and EI acquisition functions. The MACE-1
algorithm gave better performances than EI-1 and LCB-1 in the Eggholder,
Branin, Hartmann6, Ackley10, and Rosenbrock10 functions. Also, the parallel
MACE (MACE-4) gave the best performances among all the tested algorithms for
six out of the eight benchmark functions, and has shown dramatic speedup
compared to the sequential MACE (MACE-1).

@@

The operational amplifier~\cite{wang2014enabling} shown in
Figure~\ref{fig:schDAC2014} is used to test the Bayesian optimization algorithms. The circuit is designed
using the 180nm process. It has 10 design parameters, including the lengths
and widths of transistors, the resistance of the resistors and the capacitance of the
capacitors. The circuit is simulated using the commercial HSPICE circuit simulator.

We want to maximize the gain, unit gain frequency (UGF) and the phase margin (PM) for this amplifier, the Figure of Merit $FOM$ is constructed as:
$$
\mathit{FOM} = -1.2 \times \mathit{gain} - 10 \times \mathit{UGF} - 1.6 \times \mathit{PM}
$$

For this circuit, we compared the MACE algorithm with the BLCB and EI-LP
algorithms. The qKG and qEI are not compared as the computation of qEI and qKG
acquisition functions become very slow for the ten-dimensional functions.

@@

We run the algorithms in sequential mode and batch mode. For the batch mode,
the batch size is set to $B = 4$. The number of initial random sampling is set to
$N_{init} = 100$, and the number of iterations is set to $N_{iter} = 100$.

@@

The power amplifier shown in Figure~\ref{fig:schPA} is used to test the Bayesian optimization algorithms. The
circuit is designed using the 180nm process with 12 design parameters, the
circuit is simulated by the commercial HSPICE circuit simulator to get its performances.

For this power amplifier, we aim to maximize the power added efficiency (PAE) and the output power (Pout), the Figure of Merit $FOM$ is constructed as
$$
\mathit{FOM} = -3 \times \mathit{PAE} - \mathit{Pout}
$$

The MACE, BLCB, and EI-LP algorithms were tested in both sequential and batch
modes. The number of initial sampling is $N_{init} = 100$. The number of
iterations is $N_{iter} = 100$. The batch size is set to $B = 4$. The total
number of HSPICE simulations is 500 for each batch run and 200 for each
sequential run.

@@

The mean convergence plot is given in Figure~\ref{fig:resClassE}. We can see
that the MACE outperformed the BLCB and EI-LP in both sequential and batch
mode. For the batch runs, the MACE converges fastest among the three
algorithms, while the sequential MACE has similar performance as the batch
EI-LP method.
